Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-28 datapaper_calibration.tex
xm's first edits

% For one-column wide figures use
\begin{figure}
  \includegraphics[width=\linewidth,trim=50 230 45 300,clip]{Figures/CameraConfiguration}
\caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in $mm$.  The optical center of the color camera (on the left) defines the world coordinate system.  Close to it is the depth camera.  Its points are projected into the world coordinate system.  On the right is the combined fluorescent and IR camera.}
\label{fig:CameraConfiguration}
\end{figure}

%\subsection{Image Acquisition}

@@

\begin{figure*}
\centering
\begin{tabular}{ c c }
  \includegraphics[height=5.2cm,trim=160 300 170 310,clip]{Figures/BiasError} &
  \includegraphics[height=5.2cm,trim=110 240 50 260,clip]{Figures/SigmaRadius} \\
  (\emph{a}) & (\emph{b}) \\
\end{tabular}
\caption{Noise analysis for a depth camera.  (\emph{a}) Bias was fit and we found it to be roughly constant as a function of depth.  This constant offset is shown for the camera pixels with red positive and blue negative offset in mm.  Inside the chamber, the obstructions around the depth camera altered the bias somewhat and we re-calibrated the bias there.  In all cases we subtracted the modeled constant bias from the depth images.  (\emph{b}) The standard deviation of the depth camera depends on depth as well as roughly on radius from the image optical center.  A radius of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have large noise. }
\label{fig:Bias}
\end{figure*}

@@

>>>>

@@

@@

\begin{figure}
\begin{centering}
\begin{tabular}{c }
\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}\\
Arabidopsis \\
\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
   Bean \\
\end{tabular}
\caption{GRB color images of Arabidopsis and bean plants. }
\label{fig:rawIm}
\end{centering}
\end{figure}

\begin{table*}[t!]
\begin{center}
\caption{Summary of Arabidopsis and Bean databases.}
\label{tab:stat}
\begin{tabular}{c|c|c|c|c|c}
      \hline
      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
      Plants     & Subjects & Days & Images/Day & Total Images & Annotated Images \\
      \hline
      Arabidopsis &  $16$      &  $9$   &     $16$     &     $2304\times 4$     &       $576\times 4$     \\
      \hline
      Bean        &   $5$      &  $5$   &     $14$     &     $350\times 4$       &       $175\times 4$  \\
      \hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
\caption{Plant image resolution of Arabidopsis and Bean databases.}
\label{tab:resolution}
\begin{tabular}{c|c|c|c|c}
      \hline
      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
      Plants     & Fluorescence       & IR        & RGB      & Depth     \\
      \hline
      Arabidopsis &  $\sim$$240\times240$ &  $\sim$$240\times240$  & $\sim$$120\times120$  & NA  \\
      %\hline
      Bean        & $1360\times1024$ & $1360\times1024$ & $1280\times720$ & $320\times240$    \\
      \hline
\end{tabular}
\end{center}
\end{table*}

### 2015-04-28 datapaper_hardware.tex
xm's first edits

@@

In this section, we introduce the hardware used for capturing Fluorescence, IR, RGB color, and depth imagery data for both plants.

@@

@@

>>>>

\begin{figure}
  \includegraphics[width=\linewidth,trim=50 200 45 300,clip]{Figures/CameraConfiguration}
\caption{The hardware setup for our data collection. (Actual figure to be replaced)}
\label{fig:hardware}
\end{figure}

@@

In this section, we introduce the hardware used for capturing fluorescence, IR, RGB color, and depth imagery data for both plants.
Figure~\ref{fig:hardware} illustrates the hardware and imaging setup used in our data collection.

@@

% For one-column wide figures use
\begin{figure}
  \includegraphics[width=\linewidth,trim=50 230 45 300,clip]{Figures/CameraConfiguration}
\caption{A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in $mm$.  The optical center of the color camera (on the left) defines the world coordinate system.  Close to it is the depth camera.  Its points are projected into the world coordinate system.  On the right is the combined fluorescent and IR camera.}
\label{fig:CameraConfiguration}
\end{figure}

@@

\begin{figure}[t!]
\centering
%\begin{tabular}{ c c}
%  \includegraphics[height=5.2cm,trim=160 300 170 310,clip]{Figures/BiasError} &
%  \includegraphics[height=5.2cm,trim=110 240 50 260,clip]{Figures/SigmaRadius} \\
%  (\emph{a}) & (\emph{b}) \\
%\end{tabular}
\begin{tabular}{ c}
  \includegraphics[height=3.8cm,trim=175 310 140 310,clip]{Figures/BiasError} \\
   \small{(a)} \\
  \includegraphics[height=5.9cm,trim=110 250 60 260,clip]{Figures/SigmaRadius} \\
  \small{(b)}  \\
\end{tabular}
\caption{Noise analysis for a depth camera.  (\emph{a}) Bias was fit and we found it to be roughly constant as a function of depth.  This constant offset is shown for the camera pixels with red positive and blue negative offset in mm.  Inside the chamber, the obstructions around the depth camera altered the bias somewhat and we re-calibrated the bias there.  In all cases we subtracted the modeled constant bias from the depth images.  (\emph{b}) The standard deviation of the depth camera depends on depth as well as roughly on radius from the image optical center.  A radius of $200$ pixels corresponds to the corners of the depth camera, which can be seen to have large noise. }
\label{fig:Bias}
\end{figure}

### 2015-04-28 datapaper_intro.tex
xm's first edits

Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
Crop/weed &  RGB &Weed detection & Crop/weed & $2$  & $60$ & $60$ \\ \hline
\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $20$ & $XXX$ & $XXX$ \\ \cline{4-7}
							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $XXX$ & $XXX$ \\ \hline
	       \hline
	\end{tabular}
	%}
	\label{tab:database}
\end{table*}

>>>>

Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
Crop/weed &  RGB &Weed detection & Crop/weed & $2$  & $60$ & $60$ \\ \hline
\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $16$ &  $2304\times 4$ & $576\times 4$     \\ \cline{4-7}
							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $350\times 4$  &  $175\times 4$ \\ \hline
	       \hline
	\end{tabular}
	%}
	\label{tab:database}
\end{table*}

### 2015-04-28 datapapr_labeling.tex
xm's first edits

\begin{table*}
\begin{center}
\caption{Summary of Arabidopsis and Bean databases.}
\label{tab:stat}
\begin{tabular}{c|c|c|c|c|c}
      \hline
      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
      Plants     & Subjects & Days & Images/Day & Total Images & Annotated Images \\
      \hline
      Arabidopsis &  $16$      &  $9$   &     $16$     &     $2304\times 4$     &       $576\times 4$     \\
      \hline
      Bean        &   $5$      &  $5$   &     $14$     &     $350\times 4$       &       $175\times 4$  \\
      \hline
\end{tabular}
\end{center}
\end{table*}

@@

\begin{figure*}
\begin{centering}
\begin{tabular}{c c}
%\begin{tabular}{@{}c@{} c@{}}
%\begin{tabular}{lllllllll}
\includegraphics[width=.47\textwidth]{Figures/rawImages/a.png}&
\includegraphics[width=.47\textwidth]{Figures/rawImages/b.png}\\
  Arabidopsis & Bean \\
\end{tabular}
\caption{GRB color images of Arabidopsis and bean plants. }
\label{fig:rawIm}
\end{centering}
\end{figure*}

@@

\begin{table*}
\begin{center}
\caption{Plant image resolution of Arabidopsis and Bean databases.}
\label{tab:resolution}
\begin{tabular}{c|c|c|c|c}
      \hline
      % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
      Plants     & Fluorescence       & IR        & RGB      & Depth     \\
      \hline
      Arabidopsis &  $\sim$$240\times240$ &  $\sim$$240\times240$  & $\sim$$120\times120$  & NA  \\
      %\hline
      Bean        & $1360\times1024$ & $1360\times1024$ & $1280\times720$ & $320\times240$    \\
      \hline
\end{tabular}
\end{center}
\end{table*}

@@

>>>>

@@

@@

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=.98\textwidth]{Figures/overview}\\
\caption{Overview of the baseline method.}
\label{fig:methodOverview}
\end{figure*}
